---
title: "IBRA User Guide"
author: "Charlotte Soneson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{IBRA User Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

IBRA is a package to calculate and visualize performance metrics for ranking and binary assignment methods. A typical use cases could be, for example, comparing methods calling differential expression in gene expression experiments, which could be seen as either a ranking problem (estimating the correct effect size and ordering the genes by significance) or a binary assignment problem (determining which genes are differentially expressed and which are not). 

The starting point for such an evaluation is typically a collection of feature 'scores' (p-values, adjusted p-values or any other ranking score) and the truth (information about the true status, or the true scores for the features). 

## Creating a data set

```{r}
#load(system.file("extdata", "example_data.Rdata", package = "IBRA"))
#load("../data/example_data.Rdata")
#ibradata
```


```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
